Reproducible Research Peer Assignment 1
=========================================

Load the data and calculate daily steps taken
```{r}
activity<-read.csv('activity.csv')
dailysteps<-tapply(activity$steps,activity$date,sum)
```

Make a histogram of the total number of steps taken per day
```{r fig.height=4}
hist(dailysteps, xlab='Steps')
```

Calculate the mean and median total steps taken per day

```{r}
meansteps<-mean(dailysteps, na.rm=T)
mediansteps<-median(dailysteps, na.rm=T)
meansteps
mediansteps
```

Calculate and plot the average number of steps taken by time interval over all days
```{r fig.height=4}
avgsteps<-tapply(activity$steps, activity$interval, mean, na.rm=T)
intervals<-unique(activity$interval)
intervalsteps<-cbind(intervals,avgsteps)
plot(avgsteps, type='l', xlab='Intervals', ylab='Mean of Steps')
```

Which interval has the maximum number of steps (on average) across all days?
```{r}
maxsteps<-c(0,0)
for (a in 1:nrow(intervalsteps)){
  if (avgsteps[a]>maxsteps[2]){
    maxsteps[1]<-intervals[a]
    maxsteps[2]<-avgsteps[a]
  }  
}
as.integer(maxsteps[1])
```

Determine the number of NA's in the data
```{r}
x<-is.na(activity)
xna<-activity[x]
length(xna)
```

Fill in missing values with median for the given time interval
```{r}
activitynona<-activity
stepsfiller<-tapply(activitynona$steps, activitynona$interval, median, na.rm=T)
stepsfiller<-cbind(intervals,stepsfiller)
for (a in 1:nrow(activitynona)){
  if (is.na(activitynona$steps[a])){
    missinginterval=as.numeric(activitynona$interval[a])
    for (b in 1:nrow(stepsfiller)){
      if (missinginterval==stepsfiller[b,1]){
        activitynona$steps[a]=stepsfiller[b,1]
      }
    }
  }
}
```

Recalculate and plot number of steps taken daily
```{r fig.height=4}
dailystepsnona<-tapply(activitynona$steps,activitynona$date,sum)
hist(dailystepsnona, xlab='Steps',main="Daily steps with NA's replaced")
```

Recalculate the mean and median total steps taken per day

```{r}
meanstepsnona<-mean(dailystepsnona, na.rm=T)
medianstepsnona<-median(dailystepsnona, na.rm=T)
meanstepsnona
medianstepsnona
```

